### 2016-01-05 p2/conclusion.tex
New source

% Further research

Apart from constructing an algebra,
there are many other ways in which further work can extend the current results.
We think one of the most interesting extensions would be to
consider reconciling not only two, but more replicas in a single step and
prove the correctness and maximality of the algorithm proposed.
A related problem is to model cases where reconciliation cannot
complete fully
or if only a subset of the replicas are reconciled 
(e.g. due to network partitioning),
both of which would result in a state where different replicas
have different common ancestors, that is,
the updates specific to the replicas start from different points
in the update history of the filesystem.
Parker et al. (\cite{PPRS}) and Cox and Josephson (\cite{CJ})
describe version vectors (update histories) kept as metadata that could solve this problem.
Extending the algebraic approach to represent individual updates to files
in their modification histories (as described in \cite{CJ})
as separate commands could also enable it to reconcile otherwise
conflicting updates and resolve partial reconciliations.

>>>>

% Further research
% TODO Merge with other ideas?

Apart from constructing an algebra,
there are many other ways in which further work can extend the current results.
We think one of the most interesting extensions would be to
consider reconciling not only two, but more replicas in a single step and
prove the correctness and maximality of the algorithm proposed.
A related problem is to model cases where reconciliation cannot
complete fully
or if only a subset of the replicas are reconciled 
(e.g. due to network partitioning),
both of which would result in a state where different replicas
have different common ancestors, that is,
the updates specific to the replicas start from different points
in the update history of the filesystem.
Parker et al. (\cite{PPRS}) and Cox and Josephson (\cite{CJ})
describe version vectors (update histories) kept as metadata that could solve this problem,
while Chong and Hamadi present distributed algorithms that allow incremental synchronization (\cite{CH}).
Extending the algebraic approach to represent individual updates to files
in their modification histories (as described in \cite{CJ})
as separate commands could also enable it to reconcile otherwise
conflicting updates and resolve partial reconciliations.

### 2016-01-05 p2/intro.tex
New reference
New source

A central problem of command-based synchronizers 
during both update detection and reconciliation
is ordering.
If update detection is based on comparing the original state of the filesystem
to its new state, then we can easily collect a set of updates,
but we need to order these in a way that they could be applied
to the filesystems without causing an error 
(for example, a directory needs to be created before a file can be created under it).
Similarly, during reconciliation when we consider all the updates that
have been applied to the different replicas, we need to find a way of
merging these and creating a global ordering that we can apply
to the filesystems.
In fact, an insight in \cite{NREC} is that
if the ordering changes the effect of two commands (updates),
then under certain circumstances they are not compatible and will give rise to conflicts.
Accordingly, in this paper command-pairs and their properties
play a special role.
Other research also shows the essential nature of ordering:
in IceCube multiple orders are tested to find an acceptable one \cite{KRSD},
or in Bayou reconciling updates happens by redoing them in an acceptable order \cite{TTPDSH}.

>>>>

A central problem of command-based synchronizers 
during both update detection and reconciliation
is the ordering (scheduling) of commands.
If update detection is based on comparing the original state of the filesystem
to its new state, then we can easily collect a set of updates,
but we need to order these in a way that they could be applied
to the filesystems without causing an error 
(for example, a directory needs to be created before a file can be created under it).
Similarly, during reconciliation when we consider all the updates that
have been applied to the different replicas, we need to find a way of
merging these and creating a global ordering that we can apply
to the filesystems.
In fact, an insight in \cite{NREC} is that
if the ordering changes the effect of two commands (updates),
then under certain circumstances they are not compatible and will give rise to conflicts.
Accordingly, in this paper command-pairs and their properties
play a special role.
Other research also shows the essential nature of ordering:
in IceCube multiple orders are tested to find an acceptable one \cite{KRSD},
or in Bayou reconciling updates happens by redoing them in an acceptable order \cite{TTPDSH}.
Saito and Shapiro offer a survey of so-called optimistic replication algorithms in which
ordering (scheduling) plays a central role (\cite{SSH}).

### 2016-01-05 p2/references.tex
New source

% B 21
\bibitem{CBNR} 
Constantin Berzan and Norman Ramsey,
``Summer Scholars Technical Report,''
Medford, MA: Tufts University, 2010.
Accessed 29 November 2015.
http://thirld.com/files/summerscholars\undersc techreport.pdf.

% C 8
\bibitem{CJ}
Russ Cox and William Josephson,
``File synchronization with Vector Time Pairs,''
MIT CSAIL Technical Report.
Cambridge, MA: MIT,
2005.
Accessed 22 November 2015.
http://hdl.handle.net/1721.1/30527.

@@

% P 14
\bibitem{PV}
Benjamin C Pierce and J{\'e}r{\^o}me Vouillon,
``What's in Unison? A formal specification and reference implementation of a file synchronizer,''
\emph{Technical Reports (CIS),}
Paper 40.
Philadelphia, PA: U of Pennsylvania,
2004.
Accessed 23 November 2015.\\
http://repository.upenn.edu/cis\undersc reports/40.

>>>>

% B 21
\bibitem{CBNR} 
Constantin Berzan and Norman Ramsey,
``Summer Scholars Technical Report,''
Tufts University, Medford, MA, 2010.
Accessed 29 November 2015.
http://thirld.com/files/summerscholars\undersc techreport.pdf.

% C 16
\bibitem{CH}
Yek Loong Chong and Youssef Hamadi,
``Distributed Algorithms for Log-based Reconciliation,''
Microsoft Research, Microsoft Co., Redmond, WA,
Tech. Rep. MSR-TR-2004-104, 2004.

% C 8
\bibitem{CJ}
Russ Cox and William Josephson,
``File synchronization with Vector Time Pairs,''
MIT CSAIL, Cambridge, MA, 
Tech. Rep., MIT-CSAIL-TR-2005-014, 2005.
% Accessed 22 November 2015.
% http://hdl.handle.net/1721.1/30527.

@@

% P 14
\bibitem{PV}
Benjamin C Pierce and J{\'e}r{\^o}me Vouillon,
``What's in Unison? A formal specification and reference implementation of a file synchronizer,''
U of Pennsylvania,
Philadelphia, PA,
Technical Reports (CIS),
Paper 40,
2004.
Accessed 23 November 2015.\\
http://repository.upenn.edu/cis\undersc reports/40.
